Working Script

### 2020-09-01 WorkingScript.Rmd
imported new dataset with fate column
Added some graphs

```{r}
data <- read.csv("~/Desktop/MsCcHSFeedAug30.csv")
```

@@

```{r}
data <- data[data$survived == "yes", ]
```

@@

consumedsum <- consumedsum[consumedsum$ID != 707, ]
consumedsum <- consumedsum[consumedsum$ID != 1816, ]

@@

@@

```{r}
mod1 <- lmer(area ~ food + (1|bin), data = data)

>>>>

```{r}
data <- read.csv("~/Desktop/MsCcHSFeedSep1.csv")
```

@@

```{r}
data <- data[data$fate != "dead" & data$fate != "quink", ]
```

@@

@@

# Graphing

Let's graph maximum mass reached:

```{r}
ggplot(data = data, aes(x = mass.max)) + 
  geom_histogram(binwidth = 500)
```

Now, let's graph area to see if it's "normal".

```{r}
ggplot(data, aes(x = area)) + 
  geom_histogram(binwidth = 250)
```
Nope, definitely bimodal

```{r}
ggplot(data, aes(x = mass.max, y = area)) + 
  geom_point(aes(color = fate))
```

@@

```{r}
mod1 <- lm(area ~ food + fate, data = data)
